RCloud: DevOps for Visual Analysis and Data Science

### 2014-03-19 discussion.tex
yes

Shared artifacts, artifact histories, 
Discussion
View sharing - bookmarking, everything available as a URL
Content export - want to avoid, create ways of working where this is not necessary.
Social-psychological incentives - starring
Voting and ranking - starring

@@

>>>>

Returning to the design considerations outlined by Heer and Agrawala, experience with the RCloud prototype demonstrates the value of several
Shared artifacts, artifact histories, 
Discussion
View sharing - bookmarking, everything available as a URL
Content export - want to avoid, create ways of working where this is not necessary.
Social-psychological incentives - starring
Voting and ranking - starring

@@

Elaborate on to what extent can the users of the production notebooks use the tools like annotation etc. without coding or without being exposed to the analysts view. is this a gap in our design.
